Litrepl: Literate Paper Processor Promoting Transparency More Than Reproducibility

### 2025-01-02 paper/paper.tex
Update paper

\begin{figure*}[!hbt]
  \centering
  \includesvg[inkscapelatex=false,width=0.8\textwidth]{pic}
  \caption{Caption describing the image shown in the figure.}
  \label{fig:resource-allocation}
\end{figure*}

@@

The tool is implemented in Python in about 2K lines of code according to the LOC
metric, and has only two Python dependencies so far, at the cost of the
dependency on the operating system intefaces for which we choose POSIX as a
wide-spread openly available standard.

>>>>

\begin{figure*}[!hbt]
  \centering
  \includesvg[inkscapelatex=false,width=0.8\textwidth]{pic}
  \caption{Litrepl resource allocation diagram. Hash \textbf{A} is computed
  based on the Litrepl working directory and the interpreter class. Hash
  \textbf{B} is computed based on the contents of the code section.}
  \label{fig:resource-allocation}
\end{figure*}

@@

The tool is implemented in Python in about 2K lines of code according to the LOC
metric, and has only two Python dependencies so far, at the cost of the
dependency on the operating system interfaces for which we choose POSIX as a
widespread openly available standard. Needless to say, we used Litrepl to
evaluate and verify the examples presented in this document.
